|

### 2022-12-24 paper.Rmd
Sat Dec 24 00:00:06 CET 2022: update-remote.sh
Sat Dec 24 01:00:07 CET 2022: update-remote.sh

EXPERIMENT_DIR<-("../eda-gp-2020/experiments")

@@

@@

```{python pytest, , echo=FALSE, include=FALSE}
from sys import version, executable
print(f"Python Version: {version} \nPath: {executable}")
```

@@

>>>>

@@

reticulate::use_python("/Users/rmn/miniconda3/envs/dataScience/bin/python")

@@

```{python pytest, echo=FALSE}
from sys import version, executable
print(f"Python Version: {version} \nPath: {executable}")
```

@@

````{python3}
import json

S = json.load(open("./data/airfoil_FullRun_30gens/MWU-BestFitnessByGen.json", "r", encoding="utf-8"))
statistic_mwu_fitness = S["statistic"]
pval_mwu_fitness = S["p-value"]

print(pval_mwu_fitness)
````
